Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2017-04-30 methodology.tex
29-4 9-46

\subsection{Methodology}

Ten-fold-cross-validation on the total set of
machine learning methods under a subset of configurations was evaluated:

\begin{itemize}
\item Patterns: $n\times{}m$, with $n=1\ldots{}8$ and $m=1\ldots{}2$.
\TODO{No se entiende que quiere decir eso!!}
\item Methods: support vector regression with the kernels linear,
  gaussian and sigmoid; echo state networks; ordinary least squares
  linear regression, ridge regression and elastic-net regression.
  \TODO{Cada uno de esos métodos tiene a su vez un espacio
    paramétrico.  Eso tiene que quedar claro aquí: cómo se barrió el
    espacio paramétrico, para saber el nivel de detalle de la prueba!
    Eso es importantísimo, porque si no no se puede decir nada
    respecto a los métodos, sino solo respecto la configuración
    concreta probada!}
\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P ,
  \overline{W} \}$ use the subsets with one, two or four
  elements. These variables have the largest impact on the disease
  development \citep{MarinVargas1995}.
\end{itemize}

>>>>

\subsection{Methodology}
When the amount of data for training and testing is limited, is recommended
to use cross-validation \citep{Witten2011}. We used ten-fold-cross-validation 
on the total set. El diseño experimental combinó los siguientes factores:

\begin{itemize}
\item Patrones de semanas: Se formaron patrones desde tres semanas continuas
de observación para predecir una semana adelante, hasta doce semanas de
observación para predecir tres semanas adelante. Por tanto, $n\times{}m$, 
with $n=1\ldots{}12$ and $m=1\ldots{}3$.

\item techniques: support vector regression with the kernels linear,
  gaussian and sigmoid; echo state networks; ordinary least squares
  linear regression and elastic-net regression.

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P ,
  \overline{W} \}$ use the subsets with one, two, three or four
  elements. These variables have the largest impact on the disease
  development \citep{MarinVargas1995}.
\end{itemize}
